Kalman tracking and estimation of continuous gravitational waves with a pulsar timing array

### 2023-08-31 docs/manuscript/paper.tex
Bayes 2000, 10 noise realisations

\subsubsection{Multiple noise realisations} \label{sec:multiple_noise}
%\begin{figure*}
%	\includegraphics[width=\textwidth, height =\textwidth]{images/stacked_GW_plot_1000}
%	\caption{As Figure \ref{fig:corner_plot_1} but for 9 realisations of the noise processes. The inferred posterior distributions show strong agreement between the different noise realisations for the majority of static parameters. The exceptions are $\iota$ and $h$ which exhibit a larger degree of variance due to the weak identifiability between these two parameters c.f. Figure \ref{fig:likelihood_surface}.} 
%	\label{fig:corner_plot_2}
%\end{figure*}

\begin{figure*}
	\includegraphics[width=\textwidth, height =\textwidth]{images/stacked_GW_plot_small_h_definitive2}
	\caption{As Figure \ref{fig:corner_plot_1} but for 9 realisations of the noise processes. The inferred posterior distributions show strong agreement between the different noise realisations for the majority of static parameters. The exceptions are $\iota$ and $h$ which exhibit a larger degree of variance due to the weak identifiability between these two parameters c.f. Figure \ref{fig:likelihood_surface}.} 
	\label{fig:corner_plot_2}
\end{figure*}

%\begin{figure*}
%	%\centering % Not needed
%	\begin{subfigure}[b]{0.49\textwidth}
%		\includegraphics[width=\textwidth]{images/stacked_GW_plot_1000}
%		\caption{Kalman filter using correct estimate of the static parameters, $\hat{\boldsymbol{\theta}} = \boldsymbol{\theta}$ }
%		\label{fig:6MB_BFS}
%	\end{subfigure}  
%	\hfill
%	\begin{subfigure}[b]{0.49\textwidth}
%		\includegraphics[width=\textwidth]{images/stacked_GW_plot_1000}
%		\caption{Kalman filter using incorrect estimate of the static parameters, $\hat{\boldsymbol{\theta}} \neq \boldsymbol{\theta}$}
%		\label{fig:25MB_bfs}
%	\end{subfigure}
%	\caption{As Figure \ref{fig:corner_plot_1} but for 9 realisations of the noise processes. The inferred posterior distributions show strong agreement between the different noise realisations for the majority of static parameters. The exceptions are $\iota$ and $h$ which exhibit a larger degree of variance due to the weak identifiability between these two parameters c.f. Figure \ref{fig:likelihood_surface}.}
%	\label{fig:four figures2}
%\end{figure*}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{images/likelihood_surface}
	\caption{Likelihood $\log \mathcal{L}$ (Equation \ref{eq:likelihood}) surface across the $\iota - h_0$ parameter space for a single noise realisation. The red point labels the location of the likelihood maxima. The likelihood surface has been normalised with respect to the absolute value of the maxima. A strong likelihood ridge is evident in the parameter space where the Kalman filter produces similar likelihood values, making it difficult for sampling algorithms to converge to a consistent value.}
	\label{fig:likelihood_surface}
\end{figure}
%\begin{figure*}
%	\centering
%	\includegraphics[width=\textwidth]{images/compare_iotas_lines2}
%	\caption{One-dimensional marginalized posteriors for $\iota$ over 9 realisations of the noise where $h$ is (a) an unknown free parameter (left panel) and (b) fixed at its true value $= 10^{-12}$ (right panel). The thick vertical orange line labels the true injected value. The dashed vertical lines denote the median of the corresponding coloured posterior. Fixing $h$ reduces the variance between different noise realisations but results in a clear bias between the true and inferred values of $\iota$. The left hand panel is equivalent to the marginalized posteriors for $\iota$ shown in Figure \ref{fig:corner_plot_2} (4th row, 4th column), but with the $(0.16,0.84)$ quantiles replaced with the $0.5$ quantile.}
%	\label{fig:iota}
%\end{figure*}
The above discussion was for a single realisation of the noise processes. It is important to confirm that our method is robust against different realisations of the noise and that the specific realisation of the noisy data used in Sections \ref{sec:parameter_estim} is not particularly advantageous or convenient for our method. In this Section we confirm that we are able to infer comparable results for different noise realisations. To this end we take our representative example from Table \ref{tab:parameters_and_priors} and generate 1000 realisations of the process noise and measurement noise. For each realisation of the data we can then independently estimate the static parameters, $\boldsymbol{\theta}$. In Figure \ref{fig:corner_plot_2} we show the results for the  estimated values of $\boldsymbol{\theta}_{\rm gw}$ for nine realisations of the noise. This figure is analogous to the single noise realisation of Figure \ref{fig:corner_plot_1}. We plot only 9 realisations of the noise rather than the full set of 1000 realisations so as to not overcrowd the figure. As in Section \ref{sec:parameter_estim} the estimates of $\boldsymbol{\theta}_{\rm psr}$ are recovered unambiguously across the 1000 noise realisations and for brevity we do not show the results here. \newline

We can see from Figure \ref{fig:corner_plot_2} that the results from these 9 noise realisations agree well with the single realisation result that we saw in  Figure \ref{fig:corner_plot_1}. Considering the one-dimensional marginalized posteriors, the inferred probability distributions of the parameters $\Omega, \Phi_0, \psi, \delta$ and $\alpha$ broadly overlap across the different noise realisations. Moreover, the variance of each of the individual one-dimensional posteriors is generally low i.e. each of the individual distributions are narrow compared to the prior space. For each different noise realisation the method infers a consistent maximum \textit{a posteriori} probability (MAP) estimate. Conversely for the parameters $\iota$ and $h_0$ the inferred one-dimensional posteriors do not broadly overlap are not consistent across different noise realisations and the variance of an individual posterior is generally larger than for the other parameters. That is to say, we infer very different MAP estimates of these parameters depending on the particular realisation of the noise. \newline

We now consider the complete set of $10^3$ noise realisations, rather than the subset of ten realisations in the preceding discussion. For each realisation of the noise we infer a marginalised one-dimensional posterior for each parameter. We want to compare these posteriors for different noise realisations and evaluate whether our method can consistently and reliably converge to comparable posteriors.

To this end we use the the Wasserstein distance \citep[WD;][]{Wasserstein,Villani2009} from optimal transport theory which defines an intuitive notion of similarity between probability distributions. The WD is the cost of an optimal strategy for moving probability mass between two distributions from position $x$ to position $y$, with respect to some cost function $c(x,y)$. Throughout this work we use the first moment of the Wasserstein distance which for one-dimensional distributions $\mu$ and  $\nu$ is defined
\begin{eqnarray}
	W_1(\mu,\nu)=  \inf_{\lambda \in \Gamma(\mu, \nu)} \int |x-y| d \lambda (x,y)
\end{eqnarray}
where $\lambda(x,y)$ is the transport plan, $\Gamma(\mu, \nu)$ is the set of all couplings of $\mu$ and $\nu$ and $ |x-y|$ defines the cost function. The WD has an additional useful physical interpretation given by the Monge-Kantorovich duality:
\begin{eqnarray}
	| \boldsymbol{E}(X_{\mu} )-\boldsymbol{E}(Y_{\nu} ) | \leq W_1(\mu, \nu) \label{eq:WDdefn}
\end{eqnarray}
where $X_{\mu}$ and $Y_{\nu}$ are random variables of the distributions $\mu$ and $\nu$ respectively, and $\boldsymbol{E}$ denotes the expected value. We can see that the WD bounds the difference in the expected values. For example, if we compare two posteriors for $\iota$ calculated for two different noise realisations, a WD = 1.0 rad tells us that the difference in the expected value of $\iota$ from the two distributions is less than 1 rad. Beyond optimal transport theory, the WD is a popular metric in machine learning \citep{2017arXiv170107875A}, climate modelling \citep{2022JCli...35.1215P,2023QJRMS.149..843K}, computational biology \citep{GONZALEZDELGADO2023168053} and geophysics \citep{2023GeoRL..5003880M}. A full review of the Wasserstein distance, which may be unfamiliar to some readers, is presented in Appendix \ref{sec:wasserstein} \textcolor{red}{TK: is this too much info on Wasserstein? Maybe just say "its a metric between probability distributions" and move the rest to appendix so as not to interrupt main astrophysics arguments.}

For each parameter in $\boldsymbol{\theta}_{\rm gw}$ we calculate the WD between every pair of posteriors across our $10^3$ noise realisations.

@@

we consider the normalised standard deviation in the set of $10^3$ median values i.e. 
\begin{equation}
	\rho \left( \boldsymbol{\theta}\right)= \frac{1}{\mu(\boldsymbol{\theta})} \sqrt{ \frac{\sum_{i=1}^{i=10^3}\left[x_i(\boldsymbol{\theta}) - \mu(\boldsymbol{\theta}) \right]}{10^3}} 
\end{equation} 
where $\mu(\boldsymbol{\theta})$ is the mean value across the distribution of $10^3$ samples for parameter $\boldsymbol{\theta}$, and $x_i$ the value of the $i$-th sample. For the parameters $\{\Omega, \Phi_0, \psi, \delta, \alpha \}$ we have $\rho \sim \{4 \times 10^{-5}, 0.03,0.004,0.03,0.02 \}$ respectively. We can therefore see that the method is able to reliably converge to a consistent MAP estimate. Conversely, as we saw before, the MAP estimates for $\iota$ and $h_0$ are not consistent across different noise realisations, with $\rho \sim 0.3$ and $\rho \sim 0.1$ respectively. This is due to the weak-identifiability issue that we have discussed. \newline

@@

\subsection{Exploring a broader parameter space} \label{sec:parameter_space}
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{images/pp_plot_new}
	\caption{PP plot for 200 simulated GW sources for a subset of parameters of $\boldsymbol{\theta}_{\rm gw}$, randomly drawn from the prior distributions of Table \ref{tab:parameters_and_priors}. Each coloured line corresponds to a different parameter of $\boldsymbol{\theta}_{\rm gw}$. The parameters $h_0$ and $\iota$ are fixed at $5 \times 10^{-15}$ and 1.0 rad in order to maintain an approximately constant SNR. The grey shaded contours labels the $1,2,3$-$\sigma$ confidence intervals. Well estimated posteriors should fall along the diagonal $y=x$. Many parameters show evidence of being over-constrained due to a modelling bias. }
	\label{fig:parameter_space}
\end{figure}
We have so far focussed on a single representative system, summarised in Table \ref{tab:parameters_and_priors}. It is also important to test the method in different regions of the parameter space. To this end we consider 200 injections for different sets of parameter values where we fix $h_0 = 5 \times 10^{-15}$, $\iota =1.0$ and draw the remaining five parameters of $\boldsymbol{\theta}_{\rm gw}$ from the prior distributions described in Table \ref{tab:parameters_and_priors}. We fix $h_0$ and $\iota$ in order to maintain an approximately constant SNR across the parameter space. For each simulated injection we can then attempt to recover the posterior distributions for each parameter. To summarise the results across the parameter space we use a parameter-parameter (PP) plot \citep{doi:10.1198/106186006X136976}. A PP plot describes the fraction of the total number of injected parameters which are included within a given credible interval of the estimated posterior with respect to the credible interval itself. In the ideal case the PP plot should be a diagonal line, indicating that $x$-percentage of the simulated injections fall within the $x$-percentage credible interval. The results are shown in Figure \ref{fig:parameter_space}. The shaded grey contours enclose the $1\sigma$, $2\sigma$, and $3\sigma$ significance levels, given 200 injections."
We can see that only $\Omega$ falls within the $3\sigma$ shaded region. The other parameters deviate from the $y=x$ diagonal. The effect is most pronounced for $\alpha$ and $\delta$ with more modest deviations for $\psi$ and $\Phi_0$. The shape of the graph indicates that the posteriors for these parameters are over-constrained; there are fewer injections contained within high value credible intervals than would be expected statistically, and there are more injections contained within the low value credible intervals. This is an result of the bias that we observed in Section \ref{sec:multiple_noise}; the posteriors inferred for these parameters are generally highly confident, i.e. narrow, but are systematically biased away from the true injection values. This manifests in the PP plot as posteriors which are overly precise (narrow) to contain the injected value within the appropriate credible interval. An in-depth discussion on the origin of this bias is given in Section \ref{sec:bias}.

@@

%\begin{figure*}
%	\setkeys{Gin}{width=\linewidth}   
%	
%	\begin{subfigure}[b]{0.3\textwidth}
	%		\includegraphics[width=\textwidth]{images/distribution_omega_gw}
	%		\caption{$\Omega$}
	%	\end{subfigure}
%	\hfill
%	\begin{subfigure}[b]{0.3\textwidth}
	%		\includegraphics[width=\textwidth]{images/distribution_phi0_gw}
	%		\caption{$\Phi_0$}
	%	\end{subfigure}
%	\hfill	
%	\begin{subfigure}[b]{0.3\textwidth}
	%		\includegraphics[width=\textwidth]{images/distribution_psi_gw}
	%		\caption{$\psi$}
	%	\end{subfigure}
%	\medskip
%	
%	\begin{subfigure}[b]{0.3\textwidth}
	%		\includegraphics[width=\textwidth]{images/distribution_iota_gw}
	%		\caption{$\iota$}
	%	\end{subfigure}
%	\hfill
%	\begin{subfigure}[b]{0.3\textwidth}
	%		\includegraphics[width=\textwidth]{images/distribution_delta_gw}
	%		\caption{$\delta$}
	%	\end{subfigure}
%	\hfill	
%	\begin{subfigure}[b]{0.3\textwidth}
	%		\includegraphics[width=\textwidth]{images/distribution_alpha_gw}
	%		\caption{$\alpha$}
	%	\end{subfigure}
%	\medskip
%	
%	
%	\medskip
%	\begin{subfigure}[b]{0.33\textwidth}
	%		\includegraphics{images/distribution_h}
	%		\caption{$h$}
	%	\end{subfigure}
%	
%	\caption{Distribution in the median values of the 1D marginalized posteriors inferred by nested sampling for each static parameters of $\boldsymbol{\theta}_{\rm gw}$ over 1000 noise realisations. The orange dashed line labels the true injection value and the red dashed line labels the median of the distribution. \textcolor{red}{TK: these plots are ugly. Is there a better way to show this?}}\label{fig:median_distriubutins}
%\end{figure*}

>>>>

\subsubsection{Multiple noise realisations} \label{sec:multiple_noise}
\begin{figure*}
	\includegraphics[width=\textwidth, height =\textwidth]{images/stacked_GW_plot_small_h_definitive2}
	\caption{As Figure \ref{fig:corner_plot_1} but for 9 realisations of the noise processes. The inferred posterior distributions show strong agreement between the different noise realisations for the majority of static parameters. The exceptions are $\iota$ and $h$ which exhibit a larger degree of variance due to the weak identifiability between these two parameters c.f. Figure \ref{fig:likelihood_surface}.} 
	\label{fig:corner_plot_2}
\end{figure*}
The above discussion was for a single realisation of the noise processes. It is important to confirm that our method is robust against different realisations of the noise and that the specific realisation of the noisy data used in Sections \ref{sec:parameter_estim} is not particularly advantageous or convenient for our method. In this Section we confirm that we are able to infer comparable results for different noise realisations. To this end we take our representative example from Table \ref{tab:parameters_and_priors} and generate 1000 realisations of the process noise and measurement noise. For each realisation of the data we can then independently estimate the static parameters, $\boldsymbol{\theta}$. In Figure \ref{fig:corner_plot_2} we show the results for the  estimated values of $\boldsymbol{\theta}_{\rm gw}$ for nine realisations of the noise. This figure is analogous to the single noise realisation of Figure \ref{fig:corner_plot_1}. We plot only 9 realisations of the noise rather than the full set of 1000 realisations so as to not overcrowd the figure. As in Section \ref{sec:parameter_estim} the estimates of $\boldsymbol{\theta}_{\rm psr, reduced}$ are recovered unambiguously across the 1000 noise realisations and for brevity we do not show the results here. \newline

We can see from Figure \ref{fig:corner_plot_2} that the results from these 9 noise realisations agree well with the single realisation result that we saw in  Figure \ref{fig:corner_plot_1}. Considering the one-dimensional marginalized posteriors, the inferred probability distributions of the parameters broadly overlap across the different noise realisations. For the vast majority of parameters and noise realisations the injected value is contained within the 90 \% credible interval. \newline

We now consider the complete set of $10^3$ noise realisations, rather than the subset of nine realisations in the preceding discussion. For each realisation of the noise, for each parameter, we infer a marginalised one-dimensional posterior. We want to compare these posteriors for different noise realisations and evaluate whether our method can consistently and reliably converge to comparable posteriors. To this end we use the the Wasserstein distance \citep[WD;][]{Wasserstein,Villani2009} from optimal transport theory which defines an intuitive notion of similarity between probability distributions. The WD is a popular metric in machine learning \citep{2017arXiv170107875A}, climate modelling \citep{2022JCli...35.1215P,2023QJRMS.149..843K}, computational biology \citep{GONZALEZDELGADO2023168053} and geophysics \citep{2023GeoRL..5003880M}. A full review of the Wasserstein distance, which may be unfamiliar to some readers, is presented in Appendix \ref{sec:wasserstein}. The WD is the cost of an optimal strategy for moving probability mass between two distributions from position $x$ to position $y$, with respect to some cost function $c(x,y)$. Throughout this work we use the first moment of the Wasserstein distance $W_1(\mu,\nu)$ which is defined between one-dimensional probability distributions $\mu$ and $\nu$ as
\begin{eqnarray}
	W_1(\mu,\nu)=  \inf_{\lambda \in \Gamma(\mu, \nu)} \int |x-y| d \lambda (x,y)
\end{eqnarray}
where $\lambda(x,y)$ is the transport plan, $\Gamma(\mu, \nu)$ is the set of all couplings of $\mu$ and $\nu$ and $ |x-y|$ defines the cost function.  \newline

For each parameter in $\boldsymbol{\theta}_{\rm gw}$ we calculate $W_1$ between every pair of posteriors across our $10^3$ noise realisations. To form a single metric we then take the median value for each parameter across these pairwise calculations. The results are shown in Table \ref{tab:Wasserstein}.
\begin{table}
	\centering
		\begin{tabular}{ccll}
			\toprule
			Parameter & Injected Values & Units & WD  \\
			\hline
			 $\Omega$     &   $5 \times 10^{-7}$ & Hz & $10^{-9}$ \\
			 $\Phi_0$          & $0.20$ & rad & $0.13$ \\
			 $\psi$              & $2.50$ & rad & $0.16$ \\
			 $\iota$             & $1.0$ & rad & $0.14$ \\ 
			 $\delta$              & $1.0$  & rad & $0.09$ \\
			 $\alpha$          & $1.0$  & rad & $0.17$\\
			 $h_0$            & $5 \times 10^{-15}$ & - & $8 \times 10^{-16}$ \\
			\bottomrule
		\end{tabular}
		\caption{}
		\label{tab:Wasserstein}
	\end{table}
The WD has an additional useful physical interpretation given by the Monge-Kantorovich duality:
\begin{eqnarray}
	| \boldsymbol{E}(X_{\mu} )-\boldsymbol{E}(Y_{\nu} ) | \leq W_1(\mu, \nu) \label{eq:WDdefn}
\end{eqnarray}
where $X_{\mu}$ and $Y_{\nu}$ are random variables of the distributions $\mu$ and $\nu$ respectively, and $\boldsymbol{E}$ denotes the expected value. We can see that the WD bounds the difference in the expected values. For example, in Table \ref{tab:Wasserstein} we report a median $W_1 = 0.14$ rad for $\iota$. This tells us that the across all noise realisations the difference in the expected value of $\iota$ is less than 1 rad. We can see that the bounds from the WD are tight for all parameters; as a percentage of the width of the prior space, the difference in the expected values for the distributions of each parameter are $\lesssim 2 \%$.

See also Figure \ref{fig:pairwise_wasserstein}

\begin{figure*}
	\setkeys{Gin}{width=\linewidth}

	\begin{subfigure}[b]{0.22\textwidth}
			\includegraphics[width=\textwidth]{images/WD_0}
			\caption{$\Omega$}
		\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.22\textwidth}
			\includegraphics[width=\textwidth]{images/WD_1}
			\caption{$\Phi_0$}
		\end{subfigure}
	\hfill	
	\begin{subfigure}[b]{0.22\textwidth}
			\includegraphics[width=\textwidth]{images/WD_2}
			\caption{$\psi$}
		\end{subfigure}
    \hfill
	\begin{subfigure}[b]{0.22\textwidth}
			\includegraphics[width=\textwidth]{images/WD_3}
			\caption{$\iota$}
		\end{subfigure}
	\medskip
	\begin{subfigure}[b]{0.3\textwidth}
			\includegraphics[width=\textwidth]{images/WD_4}
			\caption{$\delta$}
		\end{subfigure}
	\hfill	
	\begin{subfigure}[b]{0.3\textwidth}
			\includegraphics[width=\textwidth]{images/WD_5}
			\caption{$\alpha$}
		\end{subfigure}
	\hfill	
	\begin{subfigure}[b]{0.3\textwidth}
			\includegraphics[width=\textwidth]{images/WD_6}
			\caption{$h$}
		\end{subfigure}
	\caption{Wassersteins}\label{fig:pairwise_wasserstein}
\end{figure*}

if we compare two posteriors for $\iota$ calculated for two different noise realisations, a WD = 1.0 rad tells us that the difference in the expected value of from the two distributions is less than 1 rad. \newline

Considering now the

Wd tells us only how well different distributions agreee. It doesnt tell use about the accuray of the posteriors themselves. c.f. bias

As in the singe noise case, there are tentative signs in a bias

Considering now the

$\Omega, \Phi_0, \psi, \delta$ and $\alpha$

%Moreover, the variance of each of the individual one-dimensional posteriors is generally low i.e. each of the individual distributions are narrow compared to the prior space. For each different noise realisation the method infers a consistent maximum \textit{a posteriori} probability (MAP) estimate. Conversely for the parameters $\iota$ and $h_0$ the inferred one-dimensional posteriors do not broadly overlap are not consistent across different noise realisations and the variance of an individual posterior is generally larger than for the other parameters. That is to say, we infer very different MAP estimates of these parameters depending on the particular realisation of the noise. \newline

We now consider the complete set of

@@

%
%
%we consider the normalised standard deviation in the set of $10^3$ median values i.e. 
%\begin{equation}
%	\rho \left( \boldsymbol{\theta}\right)= \frac{1}{\mu(\boldsymbol{\theta})} \sqrt{ \frac{\sum_{i=1}^{i=10^3}\left[x_i(\boldsymbol{\theta}) - \mu(\boldsymbol{\theta}) \right]}{10^3}} 
%\end{equation} 
%where $\mu(\boldsymbol{\theta})$ is the mean value across the distribution of $10^3$ samples for parameter $\boldsymbol{\theta}$, and $x_i$ the value of the $i$-th sample. For the parameters $\{\Omega, \Phi_0, \psi, \delta, \alpha \}$ we have $\rho \sim \{4 \times 10^{-5}, 0.03,0.004,0.03,0.02 \}$ respectively. We can therefore see that the method is able to reliably converge to a consistent MAP estimate. Conversely, as we saw before, the MAP estimates for $\iota$ and $h_0$ are not consistent across different noise realisations, with $\rho \sim 0.3$ and $\rho \sim 0.1$ respectively. This is due to the weak-identifiability issue that we have discussed. \newline
%
%
%
%
%

@@

\subsection{Exploring a broader parameter space} \label{sec:parameter_space}
\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{images/pp_plot_new}
	\caption{PP plot for 200 simulated GW sources for a subset of parameters of $\boldsymbol{\theta}_{\rm gw}$, randomly drawn from the prior distributions of Table \ref{tab:parameters_and_priors}. Each coloured line corresponds to a different parameter of $\boldsymbol{\theta}_{\rm gw}$. The parameters $h_0$ and $\iota$ are fixed at $5 \times 10^{-14}$ and 1.0 rad in order to maintain an approximately constant SNR. The grey shaded contours labels the $1,2,3$-$\sigma$ confidence intervals. Well estimated posteriors should fall along the diagonal $y=x$. Many parameters show evidence of being over-constrained due to a modelling bias. }
	\label{fig:parameter_space}
\end{figure}
We have so far focussed on a single representative system, summarised in Table \ref{tab:parameters_and_priors}. It is also important to test the method in different regions of the parameter space. To this end we consider 200 injections for different sets of parameter values where we fix $h_0 = 5 \times 10^{-15}$, $\iota =1.0$ and draw the remaining five parameters of $\boldsymbol{\theta}_{\rm gw}$ from the prior distributions described in Table \ref{tab:parameters_and_priors}. We fix $h_0$ and $\iota$ in order to maintain an approximately constant SNR across the parameter space. For each simulated injection we can then attempt to recover the posterior distributions for each parameter. To summarise the results across the parameter space we use a parameter-parameter (PP) plot \citep{doi:10.1198/106186006X136976}. A PP plot describes the fraction of the total number of injected parameters which are included within a given credible interval of the estimated posterior with respect to the credible interval itself. In the ideal case the PP plot should be a diagonal line, indicating that $x$-percentage of the simulated injections fall within the $x$-percentage credible interval. The results are shown in Figure \ref{fig:parameter_space}. The shaded grey contours enclose the $1\sigma$, $2\sigma$, and $3\sigma$ significance levels, given 200 injections."
We can see that only $\Omega$ falls within the $3\sigma$ shaded region. The other parameters deviate from the $y=x$ diagonal. The effect is most pronounced for $\alpha$ and $\delta$ with more modest deviations for $\psi$ and $\Phi_0$. The shape of the graph indicates that the posteriors for these parameters are over-constrained; there are fewer injections contained within high value credible intervals than would be expected statistically, and there are more injections contained within the low value credible intervals. This is an result of the bias that we observed in Section \ref{sec:multiple_noise}; the posteriors inferred for these parameters are generally highly confident, i.e. narrow, but are systematically biased away from the true injection values. This manifests in the PP plot as posteriors which are overly precise (narrow) to contain the injected value within the appropriate credible interval. An in-depth discussion on the origin of this bias is given in Section \ref{sec:bias}.

\subsection{Identifiability and bias}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{images/stacked_GW_plot_iota_h}
	\caption{}
	\label{}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{images/likelihood_surface}
	\caption{Likelihood $\log \mathcal{L}$ (Equation \ref{eq:likelihood}) surface across the $\iota - h_0$ parameter space for a single noise realisation. The red point labels the location of the likelihood maxima. The likelihood surface has been normalised with respect to the absolute value of the maxima. A strong likelihood ridge is evident in the parameter space where the Kalman filter produces similar likelihood values, making it difficult for sampling algorithms to converge to a consistent value.}
	\label{fig:likelihood_surface}
\end{figure}

@@
